
\section{Procedure}
\vspace{-0.5cm}
\singlespacing


%Free Fall

\subsection{Part 1: Elastic Collisions}

\begin{enumerate}
		\item Opened \emph{Physics Classroom - Momentum \& Collision }simulation.

		\item Set mode to "Elastic Collision".

		\item Set \textbf{blue cart }\emph{initial velocity }to 0 m/s and \textbf{red
			cart }\emph{initial velocity }to 5 m/s.

		\item Calculated \emph{initial momentum }based off masses of 1 kg for \textbf{blue
			cart }and \textbf{red cart}.

		\item Ran simulation.

		\item Calculated and recorded \emph{final momentum}.

		\item Repeated steps 3-5 but set \textbf{blue cart }to 2 kg and \textbf{red
			cart }to 1 kg. Also calculated \emph{initial kinetic energy.}

		\item Calculated \emph{final momentum }\& \emph{kinetic energy}.

		\item Calculated \emph{percent difference }between values from step 8 and the
			initial values calculated in step 7.

		\item Repeated steps 7-9 with both masses of \textbf{blue cart }and \textbf{red
			cart }set to 1 kg, \emph{initial velocity of }\textbf{\emph{red cart }}set
			to 5 m/s, and \emph{initial velocity }of \textbf{blue cart }set to -3 m/s.

		\item Repeated steps 7-9 with \textbf{red cart }at 2 kg and \textbf{blue
			cart }at 0 m/s
	\end{enumerate}

\subsection{Part 2: Inelastic Collisions}

\begin{enumerate}[resume]
		\item Set simulation mode to "Inelastic Collision"

		\item Set mass of both carts to 1 kg, \emph{initial velocity }of \textbf{red
			car }to 6 m/s, and \emph{initial velocity }of \textbf{blue car }to 0 m/s.

		\item Calculated \emph{initial momentum }and \emph{kinetic energy }in simulation.

		\item Ran simulation.

		\item Calculated \emph{final momentum }\& \emph{kinetic energy }of simulation.
			Also calculated \emph{percent difference }between \emph{initial values }calculated
			in step 14.

		\item Set mass of \textbf{blue cart }to 3 kg and \emph{initial velocity }to 0
			m/s.

		\item Repeated steps 14 - 16 for new setup.
	\end{enumerate}

\subsection{Part 3: Force During a Collision}
\begin{enumerate}[resume]
		\item Opened \emph{Logger Pro.}

		\item Set \emph{range switch }on \textbf{Force Sensor }to 10 N, and
			calibrated it using 500 g of mass.

		\item Removed \textbf{second cart }from track.

		\item Placed \textbf{clamp }mid way on track.

		\item Set \textbf{Force Sensor }against \textbf{clamp }towards \textbf{first
			cart}.

		\item Attached \textbf{elastic string }to \textbf{cart }and \textbf{Force
			Sensor}.

		\item Zeroed all sensors.

		\item Pushed \textbf{cart }away from \textbf{Force Sensor }using a gentle push.

		\item Stopped \textbf{cart }on way back to \textbf{Force Sensor}.

		\item Analyzed data using \emph{Logger Pro.}
	\end{enumerate}
\newpage




