
\section{Procedure}
\vspace{-0.5cm}
\singlespacing


%Free Fall

\subsection{Setup}

	\begin{enumerate}
		\item Added a 50\,g mass to each side of glider.
		\item Added 20\,g in increments of 5\,g to each side of the glider.
		\item Using an electronic scale, measured and recorded mass of whole system including the \textbf{glider}, \textbf{riding masses}, \textbf{mass hanger}, and \textbf{string}.
		\item Confirmed that \textbf{air supply} was connected to \textbf{glider} track and working.
		\item Placed \textbf{glider} on track, with masses parallel to track and conducted a trial run.
		\item Placed \textbf{photo gates} on track with 66 cm of space between them.
		\item Determined exactly where \textbf{photo gates} started and stopped timing, by incrementally sliding glider to each gate and marking the position where the timers activated as \textit{x1} and \textit{x2} respectively.
		\item Repeated step 7 four times until measurements were precise to the nearest millimeter.
		\item Placed tape on \textbf{photo gates} to lock them in place.
		\item Set \textbf{photo timer} mode to \textit{PULSE}. 
	\end{enumerate}	

\subsection{Data Collection}

	\begin{enumerate}[resume]
		\item Placed one 5.0\,g mass taken from the \textbf{glider} onto the \textbf{hanger}.
		\item Recorded mass of \textbf{hanger} with added weight. 
		\item Brought \textbf{glider} to \textit{x1} and held it in place.
		\item Turned on \textbf{air supply}.
		\item Waited three seconds before releasing \textbf{glider}. 
		\item Recorded time between \textbf{photo gate timers}.
		\item Repeated steps 13-16 two more times.
		\item Repeated steps 11-17 until 40\,g of mass were on the \textbf{hanger}.
	\end{enumerate}

\newpage




